\section{Threats to Validity}\label{sec:validity}

\noindent {\textbf{Internal Validity}} The experience difference in two group could have affected the response time and result of the evaluation. %Participants are encouraged to perform the program transformation proposals in the experimental group. 
%\textbf{Construct Validity} 


\noindent {\textbf{External Validity}}  All the participants are graduate or undergraduate students in University of Texas at Austin major in Computer Science or Software Engineering. Although the participants have diverse experiences in Java, refactoring and Eclipse IDE, they might not be representative of all software developers in industry. Our recommendation tool is also confined with the Eclipse and supports Java only. 

\section{Discussion and Future Work}\label{sec:discussion}


\section{Conclusion}\label{sec:conclusion}
In this paper, we present the preliminary result of our IDE recommendation for systematic edits using edit recipes learned from examples. We describe our approach to match, filter, evaluate the consequence of the program transformation  and display the candidate proposal list with content assist engine in Eclipse with preview and consequence preview aside. Our tool eliminates the tedious invoking and configuration process for the program transformation with a safe consequence evaluation of potential compilation errors for the systematic change. Our experiment on the Eclipse SWT project illustrates that SyditRecommender is able to detect and apply the similar but not identical systematic edits with an accuracy of X\%. The user study we conduct prove that SyditRecommender  is more intuitive than the traditional program transformation tools with a X\% efficiency improvement on average. 


